---
title: "Cyclistic Bikes: User Performance"
author: "Lorena Méndez"
date: "April 25th, 2022"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

## Why converting casual members into annual members is possible??....

We used available data to find some connections or patterns in how our members using Cyclistic Bikes differently.

## Prepare and Clean Data

Explore our date is the most and important step in our analysis.

```{r Read cvs files}
a <- read.csv("202201-divvy-tripdata.csv")

colnames(a)
str(a)
```

We worked with data from April 2021, to March 2022. Those all data was in `.csv` files and we combine the information into a single file. For example:

``` yaml
##Quarters

mar_2022 <- read_csv("202203-divvy-tripdata.csv")
feb_2022 <- read_csv("202202-divvy-tripdata.csv")
jan_2022 <- read_csv("202201-divvy-tripdata.csv")

q1 <- bind_rows(jan_2022, feb_2022, mar_2022)
```

This exercise we did with the remaining 9 months.

## Clean Up and Add Data

After review our columns for our analysis just using the columns related our problem, for that reason we eliminate some information:

    q1 <- q1 %>% 
      select(-c(start_station_name, start_station_id, end_station_name, 
                end_station_id, start_lat, start_lng, end_lat, end_lng))

After all this process we get just one file clean and ready to use called: `annualv2`

```{r Read csv file}
annualv2 <- read.csv("annualv2.csv")

```

### 1. Add columns that list the date, month, day, and year of each ride.

    annual$date <- as.Date(annual$started_at)
    annual$month <- format(as.Date(annual$started_at), "%m")
    annual$day <- format(as.Date(annual$started_at), "%d")
    annual$year <- format(as.Date(annual$started_at), "%Y")
    annual$day_of_week <- format(as.Date(annual$started_at), "%A")

### 2. Add a "ride_length" calculation (in seconds)

    annual$ride_length <- difftime(annual$ended_at,annual$started_at)

```{r Colnames annualv2}

colnames(annualv2)
```

### 3. Remove bad data (negative results)

    is.factor(annual$ride_length)
    annual$ride_length <- as.numeric(as.character(annual$ride_length))
    is.numeric(annual$ride_length)

    annualv2 <- annual[!(annual$ride_length<0),]

After all this process we get just one file clean and ready to use called: `annualv2`

```{r head annualv2}

head(annualv2)
```

## Descriptive Analysis

### 1. Descriptive analysis on ride_lenght

```{r Descriptive analysis}
mean(annualv2$ride_length)
median(annualv2$ride_length)
max(annualv2$ride_length)
min(annualv2$ride_length)

```

In summary,

```{r summary annualv2}

summary(annualv2$ride_length)
```

### 2. Ride_lenght by type of user

For our client is important to know which is the average by type of user, this information is consolidate in seconds (sec).

```{r Average by user type in seconds}
an2 <- aggregate(annualv2$ride_length ~ annualv2$member_casual, FUN = mean)
head(an2)
```



## Stay Tuned

Please visit my [**website**](https://lorenamendezg.github.io/) to know about me, my projects and my new road for the data world. Comments, bug reports and pull requests are always welcome.
